Statistical Reporting Inconsistencies in Experimental Linguistics

### 2024-07-29 manuscript/manuscript.tex
residual fixes

\abstract{The present paper investigates the prevalence of statistical
reporting consistencies across articles in eight experimental
linguistics journals, published between 2000 and 2023. Using the R
package ``Statcheck'', we retrieved 39532 statistical test and assessed
whether p-values were inconsistent with their test statistic and degrees
of freedom. Half of all articles that used null hypothesis signficance
testing contained at least one inconsistent p-value. One in eight
articles contained an inconsistency that may have affected the
statistical conclusion. The inconsistency rates were stable across
journals and publication years. We offer actionable steps for authors,
reviewers, and editors to remmedy this state-of-affairs.}

\keywords{statistics, statcheck, reproducibility}

\authornote{\par{\addORCIDlink{Timo B. Roettger}{0000-0000-0000-0001}} 
\par{ }
\par{   The authors have no conflict of interest to
declare.   Conceptionalization, Methodology, Validation, Formal
Analysis, Review \& Editing of Manuscript, Data Curation - T.B.R. \&
D.L.J.E.; Software, Investigation - D.L.J.E.; Writing of Original Draft,
Visualization, Supervision - T.B.R. }
\par{Correspondence concerning this article should be addressed to Timo
B. Roettger, Email: timo.roettger@gmail.com}
}

>>>>

\abstract{The present paper investigates the prevalence of statistical
reporting consistencies across articles in eight experimental
linguistics journals published between 2000 and 2023. Using the R
package ``Statcheck'', we retrieved 39532 statistical test and assessed
whether p-values were consistent with their test statistic and degrees
of freedom. Half of all articles that used null hypothesis significance
testing contained at least one inconsistent p-value. One in eight
articles contained an inconsistency that may have affected the
statistical conclusion. The inconsistency rates were comparable across
journals and seem stable over publication years. We discuss possible
reasons for this high rate and offer actionable steps for authors,
reviewers, and editors to remedy this state-of-affairs.}

\keywords{statistics, statcheck, reproducibility, null hypothesis
significance testing}

\authornote{\par{\addORCIDlink{Timo B. Roettger}{0000-0000-0000-0001}} 
\par{ }
\par{   The authors have no conflict of interest to
declare.   Conceptionalization, Methodology, Validation, Formal
Analysis, Review \& Editing of Manuscript, Data Curation - T.B.R. \&
D.L.J.E.; Software, Investigation - D.L.J.E.; Writing of Original Draft,
Visualization, Supervision - T.B.R. }
\par{Correspondence concerning this article should be addressed to Dara
Leonard Jenssen Etemady, Email: daraetemady@gmail.com}
}
